---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

`tinyjs` - Lightweight Embedded JavaScript Engine (a wrapper for [TinyJS](https://github.com/gfwilliams/tiny-js))

An R interface to the 'TinyJS' — <https://github.com/gfwilliams/tiny-js> — JavaScript engine; a more lightweight alternative to 'V8' with no external dependencies.

The following functions are implemented:

- `source_js` : source a javascript file
- `eval_js` : evaluate javascript strings
- `js_get` : get javascript objects

The following data sets are included:

- `system.file("js/test001.js", package="tinyjs")`
- `system.file("js/test002.js", package="tinyjs")`
- `system.file("js/test003.js", package="tinyjs")`
- `system.file("js/test004.js", package="tinyjs")`
- `system.file("js/test005.js", package="tinyjs")`
- `system.file("js/test006.js", package="tinyjs")`
- `system.file("js/test007.js", package="tinyjs")`

### News

- Version 0.2.5.9000 99.9% CRAN checks & added tests + built w/`build_win()`
- Version 0.2.0.9000 cleaner API
- Version 0.1.0.9000 released

### Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/tinyjs")
```

```{r echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
options(width=120)
```

### Usage

```{r}
library(tinyjs)

# current verison
packageVersion("tinyjs")

eval_js("var a=10;")
js_get("a")

eval_js("var b={this:'that', or:4, the:['ot', 'he', 'r']};")
js_get("b")

for(js_fil in sprintf("js/test00%d.js", 1:7)) {
  source_js(system.file(js_fil, package="tinyjs"))
  print(js_get("result"))
}
```

### Test Results

```{r}
library(tinyjs)
library(testthat)

date()

test_dir("tests/")
```

### Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). 
By participating in this project you agree to abide by its terms.
